Rates of true polar wander in convecting planets

### 2015-09-02 tpw_rate.tex
Update reference

%in case I want to add detail to any derivation
\newif\ifdetail
%\detailfalse
\detailtrue

@@

We performed a series of numerical simulations of mantle convection at different Rayleigh numbers to test this scaling.
We used the mantle convection software \texttt{ASPECT} \citep{kronbichler2012high}, based on the finite element library \texttt{deal.II} \citep{dealII81}.
which allows for flexible implementation of 
In order to test a wide range of Rayleigh numbers, we ran the simulations in a 2D annulus, tracking the eigenvalues of the 
moment of inertia tensor and integrating Equation~\eqref{eq:liouville_ode} in time.
For the 2D simulations there is a reduced dimensionality when calculating the number of modes,
so $N_\mathrm{modes} \sim \left(R/d \right)^2$.  This leads us to a scaling of $T_{\mathrm{degree\textendash two}} \sim \mathrm{Ra}^{-2/3}$, which is used in the simulations shown in Figure~\ref{fig:eigengap}.
This result has a simple interpretation.
As the Rayleigh number of the system increases, the smallest lengthscale of convective features gets smaller.
The total power in the temperature field is spread across a larger spectrum, leaving less total power for the degree-two part, which is what drives TPW.

>>>>

%in case I want to add detail to any derivation
\newif\ifdetail
\detailfalse
%\detailtrue

@@

We performed a series of numerical simulations of mantle convection at different Rayleigh numbers to test this scaling.
We used the mantle convection software \texttt{ASPECT} \citep{kronbichler2012high}, based on the finite element library \texttt{deal.II} \citep{dealII82}.
which allows for flexible implementation of 
In order to test a wide range of Rayleigh numbers, we ran the simulations in a 2D annulus, tracking the eigenvalues of the 
moment of inertia tensor and integrating Equation~\eqref{eq:liouville_ode} in time.
For the 2D simulations there is a reduced dimensionality when calculating the number of modes,
so $N_\mathrm{modes} \sim \left(R/d \right)^2$.  This leads us to a scaling of $T_{\mathrm{degree\textendash two}} \sim \mathrm{Ra}^{-2/3}$, which is used in the simulations shown in Figure~\ref{fig:eigengap}.
This result has a simple interpretation.
As the Rayleigh number of the system increases, the smallest lengthscale of convective features gets smaller.
The total power in the temperature field is spread across a larger spectrum, leaving less total power for the degree-two part, which is what drives TPW.
